Survival Analysis

### 2014-04-03 presentation.Rnw
Oh shit: truncate, don't throw away data!
More fixing derps

# FDA recommends 6 months of breastfeeding ~ 27 weeks
bfeed.short <- subset(bfeed, duration < 32)
@

@@

\scriptsize
<<bfeed-test-correspondence>>=
survdiff(Surv(duration, delta) ~ poverty, data = bfeed.short)
@
\end{frame}

@@

\tiny
<<bfeed-test-single>>=
summary(coxph(Surv(duration, delta) ~ yschool > 12, data = bfeed.short))
@
\end{frame}

>>>>

# FDA recommends 6 months of breastfeeding ~ 27 weeks
bfeed.short <- bfeed
bfeed.short$duration <- with(bfeed.short, ifelse(duration > 36, 36, duration))
@

@@

\scriptsize
<<bfeed-test-correspondence>>=
survdiff(Surv(duration, delta) ~ poverty, data = bfeed)
@
\end{frame}

@@

\tiny
<<bfeed-test-single>>=
summary(coxph(Surv(duration, delta) ~ yschool > 12, data = bfeed))
@
\end{frame}
